Summer 2024 Report

### 2024-09-05 Relations/Report.tex
recurrence
ARS stuff

\end{document}

>>>>

\section{Notes from 08.29}

\begin{enumerate}
  \item Try to ``fix'' CP by changing $R$ into $R^r$
  \item Finish formulating the ``compactness property".  Two candidates:
  \begin{itemize}
    \item ``Every cocone for a given infinite sequence loops back to some point in the sequence"
    \item ``If an $R^*$-sequence has a cocone then it's constant after some point on.''
  \end{itemize}
  \item Add the definition of "recurrent element"
\end{enumerate}

\section{09.05}
\begin{enumerate}
  \item done: WN, UN, RP imply SN (classical)
  \item need: omega bounded and RP implies SN (classical)
  \item need: omega bounded and RP implies SN (constructive)
  \item do we need $s_0 \to^* s_c$ in the proof?
  \item is $\omega$-bounded implied by WN and the following confluence property:
  $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $.
  \item Remark before 1.2? (Exercise 1.3.21)
  \item Make the first argument to "being a normal form" implicit?
\end{enumerate}
\end{document}
